\chapter{User and competitive Analysis} 

\section{User Analysis}

\paragraph{}
Due	to	health	data	pollution	on	the	Internet,	it	is	very	difficult	for	people	to	access	reliable	healthcare	data.	Because	of	the	potential	panic	of	data	pollution	and	the	inability	to	respond	to	every	incoming	question,	customization	is	essential	to	respond	to	this	need.	In	this	context,	the	main	target	audience	for	this	application	is	any	user	who	needs	information	about	health.	The	advantages	of	the	application	can	be	listed	as	follows:
\begin{itemize}
	\item Reliable	health	information	data;
	\item Accurate	treatment	for	the	complaint;
	\item Reduced	time	effort;
	\item User-friendly	interface.
\end{itemize}

\section{Competitive	Analysis	}

\paragraph{}
There	are	four	successful	projects	in	this	area,	three	from	the	UK	and	one	from	the	People's	Republic	of	China.		

\paragraph{Your	Md.:}This	application,	which	has	been	on	the	market	with	the	support	of	the	UK	Ministry	of	Health,	draws	symptoms	from	the	user's	text	and	asks	for	more	detailed	questions.	As	a	result	of	the	estimation,	detailed	information	is	given	about	prominent	diseases	and	treatments.	

\paragraph{Babylon	Health:}This	UK-based	application	is	also	collecting	data	similar	to	your	Md.	In	addition,	there	is	the	possibility	of	paid	consultation	to	a	doctor	by	voice	or	video.	

\paragraph{Ada	Health:}Unlike	the	other	two	applications,	the	user	selects	a	symptom	from	a	search	made	with	the	help	of	key	words,	not	the	text,	and	asks	users	questions	based	on	them.	At	the	same	time,	the	application	has	the	ability	to	train	itself	by	storing	user	data.	

\paragraph{Baidu	Melody:}The application	claims	that	Baidu	developers	have	succeeded	in	creating	a	powerful	medical	assistant	with	advanced	depth	learning	and	natural	language	processing	skills.	However,	this	practice	can	only	be	used	on	the	borders	of	the	People's	Republic	of	China.	

Unlike	other	applications	in	our	project,	what	we	want	to	do	is	to	get	all	of	the	complaints	from	the	entered	text,	reduce	the	time	to	diagnose	and	increase	the	accuracy.			
